Preliminary Draft

### 2021-07-26 article/draft.tex
section 5.1 in the discussion

Aside from the lack of data availability due to account or channel suspensions, some essential metrics for the study of misinformation are not accessible via main APIs. In particular, the $reach$ of posts on Facebook cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example). Furthermore, to the best of our knowledge, fields related to flags, notices, interstitials and information panels are not available on the APIs linked to Facebook, Twitter and YouTube. For the purposes of the present research we had to scrape this information (see section \ref{flags}). Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact.

@@

{\bf Lack of transparency.} Second, mainstream platforms generally lack transparency regarding their misinformation related interventions.  The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}). For example, Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explains its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}). Nevertheless, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube. To provide an example, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content. More precisely, the academic community can only be aware of interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets. For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended, yet there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).

Finally, we are aware that full transparency regarding how misinformation related interventions are operated, can backfire, as the prospective aimed users might find means to circumvent the partly automated interventions. To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}). Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''.  Hence, a balance is needed between fully transparent communication about misinformation related interventions so the users can know precisely, how the platforms are regulating their content, and not explicitly giving too much information which would allow the policies to be bypassed.

>>>>

Aside from the lack of data due to account or channel suspensions, some essential metrics for the study of misinformation are not accessible via main APIs. In particular, the $reach$ of posts on Facebook cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example). Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the APIs linked to Facebook, Twitter and YouTube. For the purposes of the present research we had to scrape this information (see section \ref{flags}). Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact.

@@

{\bf Lack of transparency.} Second, mainstream platforms generally lack transparency regarding their misinformation related interventions.  The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}). For example, Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explains its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}). Nevertheless, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube. To provide an example, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content. More precisely, the academic community can only be aware of interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets. For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended. Yet, there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).

Finally, we are aware that full transparency regarding operational aspects of misinformation related interventions can backfire. This is because, the prospective aimed users might find means to circumvent the partly automated interventions. To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}). Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''. Similarly, we came across  notational variants on Twitter of domain names with several failed fact-checks. To provide an example, Twitter users introduce  the following notational variants when sharing an article from the website\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}} {\it off-guardian.org}: {\it off-guardian. org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}. For the case of this domain name, we successfully managed to post a Tweet containing the domain name {\it off-guardian.org}, which we deleted after a few seconds. In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link. For this case, we failed to understand precisely what kind of intervention the users were circumventing. Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
